Data Migration under a Changing Schema in Ampersand

### 2023-10-18 2022Migration/articleMigrationFACS.tex
minor

\section{Generating a Migration Script}
   A migration script takes care of two things: copying data and ensuring that the migration system is a proper information system.
\subsection{Generating a migration script}
   In the migration system, we need to refer to the items (concepts, relations, and constraints) of both the existing system and the desired system.
   We use a prime symbol to denote the elements of the desired system, so $\infsys$ is the existing system and $\infsys'$ is the desired system.
   We also have to relabel items with prefixes to avoid name clashes in the migration system.
   We use a left arrow to denote relabeling by prefixing the name of the item with ``old.''.
\begin{equation}
   \begin{array}[m]{rcl}
      \overleftarrow{\pair{\dataset}{\schema}}&=&\pair{\overleftarrow{\dataset}}{\overleftarrow{\schema}}\\
      \overleftarrow{\pair{\triples}{\instance}}&=&\pair{\overleftarrow{\triples}}{\instance}\\
      \overleftarrow{\quintuple{\concepts}{\rels}{\rules}{\transactions}{\busConstraints}}&=&\quintuple{\concepts}{\overleftarrow{\rels}}{\overleftarrow{\rules}}{\overleftarrow{\transactions}}{\overleftarrow{\busConstraints}}\\
      \overleftarrow{\triples}&=&\{\triple{a}{\overleftarrow{r}}{b}\mid\triple{a}{r}{b}\in\triples\}\\
      \overleftarrow{\declare{n}{A}{B}}&=&\declare{old.n}{A}{B}\\
      \overleftarrow{X}&=&\{\overleftarrow{x}\mid x\in X\}\\
      \viol{\overleftarrow{u}}{\overleftarrow{\dataset}}&=&\viol{u}{\dataset}\\
      \sign{\overleftarrow{u}}&=&\sign{u}\\
      \enfRel{\overleftarrow{u}}&=&\overleftarrow{\enfRel{u}}
   \end{array}
\end{equation}
   The notation $\overrightarrow{\infsys}$ is defined similarly, using prefix ``new.'' instead of ``old.''.

>>>>

\section{Generating a Migration Script}
   A migration script takes care of two things: copying data and ensuring that the migration system is a proper information system.
\subsection{Generating a migration script}
   In the migration system, we need to refer to the items (concepts, relations, and constraints) of both the existing system and the desired system.
   We have to relabel items with prefixes to avoid name clashes in the migration system.
   We use a left arrow to denote relabeling by prefixing the name of the item with ``old.''.
\begin{equation}
   \begin{array}[m]{rcl}
      \overleftarrow{\pair{\dataset}{\schema}}&=&\pair{\overleftarrow{\dataset}}{\overleftarrow{\schema}}\\
      \overleftarrow{\pair{\triples}{\instance}}&=&\pair{\overleftarrow{\triples}}{\instance}\\
      \overleftarrow{\quintuple{\concepts}{\rels}{\rules}{\transactions}{\busConstraints}}&=&\quintuple{\concepts}{\overleftarrow{\rels}}{\overleftarrow{\rules}}{\overleftarrow{\transactions}}{\overleftarrow{\busConstraints}}\\
      \overleftarrow{\triples}&=&\{\triple{a}{\overleftarrow{r}}{b}\mid\triple{a}{r}{b}\in\triples\}\\
      \overleftarrow{\declare{n}{A}{B}}&=&\declare{old.n}{A}{B}\\
      \overleftarrow{X}&=&\{\overleftarrow{x}\mid x\in X\}\\
      \viol{\overleftarrow{u}}{\overleftarrow{\dataset}}&=&\viol{u}{\dataset}\\
      \sign{\overleftarrow{u}}&=&\sign{u}\\
      \enfRel{\overleftarrow{u}}&=&\overleftarrow{\enfRel{u}}
   \end{array}
\end{equation}
   The notation $\overrightarrow{\infsys}$ is defined similarly, using prefix ``new.'' instead of ``old.''.
